July 19 2013 Seattle WA
Knitr and ReportingTools 
===============================================

       
Here we will create a simple report that integrates `ReportingTools` report capabilities with knitr.

To build this report, simply call the `knit2html` function from the
knitr package.
* By default, knitr will write the destination file within the current working directory. 
* We thus call `knit2html` from within the 
   `reportDirectory`. 
* Alternatively, we can call `knit2html` with an
   `output` argument that matches the `reportDirectory`
   argument passed to `HTMLReport`.   
   
   
We run this page via the following code:
library(knitr); 
setwd("reports"); 
knit2html("/data/ReportingToolsWorkshop/4BioCknitr.Rmd")

We begin our report by loading the `ReportingTools` package and `iris` data.
```{r message=FALSE, results="asis"}
library(ReportingTools)
##data(iris)
```

We now publish our data frame as a table through the use of the knitrHandlers.

We do not call finish since we plan to add additional output to this knitr report.

```{r results="asis"}
library(XML)
htmlRep <- HTMLReport(shortName = "knitrReport", handlers=knitrHandlers,
                      reportDirectory = './reports')
publish(iris, htmlRep)
```

We are thus able to include tables generated by ReportingTools based directly within knitr documents.

Next we add a link, an image and some text with the help of hwriter:
```{r results = "asis"}
library(hwriter)
publish(hwrite('This is a link to Bioconductor', link = 'http://www.bioconductor.org'), htmlRep)
publish(hwrite('Scatterplot of results', heading=3), htmlRep)
himg <- hwriteImage('xyplot.png', link='xyplot.png', width=100)
publish(hwrite(himg, br=TRUE), htmlRep)
```

As we have seen, using ReportingTools in conjunction with knitr is as easy as selecting a different set of ReportHandlers and ensuring that the location of the final HTML file is the same as what is specified in our call to HTMLReport.

This allows us to create rich knitr-based reports and vignettes while leveraging the power of ReportingTools to format and display generated R objects.

