Compute Gene Network
========================================================

```{r, results='hide', message=FALSE}
library(Biobase)
library(ENA)
library(shiny)
```

## Reconstruct the Full Network

We'll take advantage of the ENA (Ensemble Network Aggregation) package to reconstruct the gene expression network we already loaded.

```{r}
# Load in the sampled matrices we've generated ahead of time.
tumor <- readRDS("tumorExpr.Rds")
# Distill the expression data away from the ExpressionSet object.
tumorExp <- exprs(tumor)

# Reconstruct the gene network. Note that this could potentially be
# distributed across a compute cluster.
gn <- buildWgcna(tumorExp)
```

## Filter the Graph Edges

We'll take a quick look at the distribution of the edge weights in the generated network.

```{r}
weights <- abs(gn)[upper.tri(gn)]
hist(weights)
summary(weights)
```

We'll now filter the edges to only include strong connections.

```{r}
cutoff <- runApp()
filtered <- abs(gn) > cutoff
```

## Write the Output

We'll finally write out the adjacency matrix as a CSV file.

```{r}
write.csv(mat2adj(filtered), file="geneNet.csv")
```
