Extract and Store Some Data
========================================================

We'll first want to install the `curatedOvarianData` package from Bioconductor. Note that this package is a few hundred MB.

```{r, cache=TRUE, results='hide', message=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("curatedOvarianData")
```

Now we'll load the package and load in one of the datasets.

```{r, results='hide', message=FALSE}
library(curatedOvarianData)
data(TCGA_eset)
```

Let's write out the clinical data so we have it for later. We'll trim out the "uncurated" metadata column to save some space and make the printing a bit easier.

```{r}
clinical <- phenoData(TCGA_eset)
pData(clinical) <- pData(clinical)[,colnames(pData(clinical))!="uncurated_author_metadata"]
```

We won't want to store all of the tumor samples available in the dataset, so let's grab 50 tumor samples at random and keep all of the normal samples.

```{r}
# Get all normal phenotypic data
normalClinical <- clinical
pData(normalClinical) <- pData(clinical)[pData(clinical)$sample_type == "adjacentnormal",]

# Sample 20 samples from the tumor phenotypic data
tumorIndices <- sample(which(pData(clinical)$sample_type == "tumor"), 50)
tumorClinical <- clinical
pData(tumorClinical) <- pData(clinical)[tumorIndices,]
```

Filtering
---------

For the sake of demonstration, we'll want to keep the dataset fairly small. So let's filter the data to the few dozen samples we selected above and only 8 genes.

```{r}
# Provide the HGNC symbols of 8 genes
geneList <- c("EGFR", "KLF6", "FOXO1", "KRAS", "JAK2", "BRCA1", "BRCA2", "PPM1D")

# Extract the relevant probeset to gene mappings
featureList <- fData(TCGA_eset)
featureList <- featureList[featureList$gene %in% geneList, ]
featureList <- featureList[match(geneList, rownames(featureList)), ] #order
featureList <- AnnotatedDataFrame(featureList)

# Filter the tumor expression data to only relevant genes and samples
tumor <- exprs(TCGA_eset[,tumorIndices])
tumor <- tumor[match(geneList, rownames(tumor)),]
tumor <- ExpressionSet(tumor, tumorClinical, featureList, experimentData(TCGA_eset))
saveRDS(tumor, "tumorExpr.Rds")
```

And grab all of the normal tissue samples:

```{r}
# Filter the normal expression data to only relevant genes and samples
normal <- exprs(TCGA_eset[,TCGA_eset@phenoData@data$sample_type == "adjacentnormal"])
normal <- normal[match(geneList, rownames(normal)),]
normal <- ExpressionSet(normal, normalClinical, featureList, experimentData(TCGA_eset))
saveRDS(normal, "normalExpr.Rds")
```

Now we should be able to use this sampled data from our apps!
